Malacology: A Programmable Storage System

### 2016-10-18 paper/paper.tex
updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

%\usepackage{fullpage}
%\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
%\usepackage{amssymb,amsmath}
%\usepackage{ifxetex,ifluatex}
\usepackage{amsmath}
%\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{listings}
%\usepackage{amssymb}
\usepackage{pifont}
\usepackage{color}
\newcommand{\cmark}{\ding{51}}%

@@

\begin{table*}
\centering
\begin{tabular}{  l | l | l | l }
\multicolumn{4}{c}{\Large \textbf{Common Internal Abstractions}} \\
\multicolumn{4}{c}{} \\
\textbf{Abstraction}                    &
\textbf{Example in Production Systems}  &
\textbf{Example in Ceph}                &
\textbf{Provided Primitives}            \\ \hline
{\it Service Metadata}
  & Zookeeper coordination~\cite{hunt_zookeeper_2010}, Chubby~\cite{website:chubby}
  & cluster state management~\cite{website:ceph-mon}
  & consensus \& consistency
  \\
{\it Shared Resource}
  & MPI collective IO, burst
  & POSIX metadata protocols~\cite{CITEME}
  & serialization \& batching
  \\
{\it Object \& Data}
  & Swift in situ storage/compute~\cite{website:zerocloud}
  & object interface classes~\cite{website:cls-lua}
  & transaction \& atomicity
  \\
Durability
  & S3/Swift interfaces (RESTful API)
  & object store library~\cite{weil_rados_2007}
  & interface to persistence
  \\
Load Balancing
  & VMWare's VM migration~\cite{vmware-drs,gulati:hotcloud2011-cloud-resource-management} 
  & migration in metadata cluster~\cite{weil:sc2004-dyn-metadata}
  & migration \& sampling
  \\
Beacon
  & Apache RabbitMQ~\cite{CITEME}
  & inter-daemon messages, centralized logging
  & debugging \& monitoring
  \\
\end{tabular}
\caption{The same ``internal abstractions" are common across large-scale
systems because they provide primitives that solve general distributed systems
problems.  Here we list examples of what these internal abstractions are used
for in ``production systems" and in Ceph.  Malacology provides these internal
abstractions as interfaces that higher level applications can use; {\it
italicized abstractions} are interfaces contributed in this paper.}
\label{table:examples}
\end{table*}

@@

The default behavior of the monitor can be seen as a Paxos-based notification
system, similar to the one introduced in~\cite{burrows_chubby_2006}, allowing
clients to identify when new values (termed epochs in Ceph) are associated to
given maps.  While Ceph does not expose this service directly, a key-value
service designed for managing configuration metadata that is built on top of
the consensus engine is an example of a high-level service within Ceph that
re-uses existing abstractions.  While a key-value service is generally useful,
it doesn't provide many of the useful services hidden within the monitoring
framework that would be required for applications with more demanding
requirements, such as creating arbitrary maps or associating
application-specific logic that can be executed for particular maps (or values
in a map).  Since the monitor is intended to be out of high-performance I/O
paths, a general guideline is to make use of this functionality infrequently
and to assign small values to maps.

\paragraph*{Malacology:} Malacology exposes a strongly-consistent view of
time-varying service metadata as a service rather than a hidden internal
component. Malacology provides a generic API for adding arbitrary values to
existing subsystem cluster maps. As a consequence of this, applications can
define simple but useful service-specific logic to the strongly-consistent
interface, such as authorization control (just specific clients can write new
values) or to trigger actions based on specific values (e.g. sanitize values).
The higher level services we implement in \S\ref{sec:services} make use of this
functionality to register, version and propagate dynamic code (Lua scripts) for
new object interfaces defined in storage daemons (\S\ref{active-storage}) and
policies in the load balancer \S\ref{malacology:mds}).  Using this service
guarantees that interface definitions are not only made durable, but are
transparently and consistently propagated throughput the cluster and that
clients are properly synchronized with the latest interfaces.

@@

\subsection{Object \& Data Interface}
\label{object-data-interface}

@@

An object interface is a plugin structured in a similar way to that of an RPC
in which a developer creates a named function within the cluster that clients
may invoke. In the case of Ceph each function is implicitly run within the
context of an object specified when the function is called. Developers of
object interfaces express behavior by creating a composition of native
interfaces or other custom object interfaces, and handle serialization of
function input and output. A wide range of native interfaces are available to
developers, such as reading and writing to a byte stream, and controlling
snapshots and clones. These object interfaces may be transactionally composed
with access to a sorted key-value service allowing applications to create rich
semantics. An example is using a read-modify-write guard to protect a shared
index defined over content stored in a byte stream.

@@

To address these concerns, Malacology takes advantage of Lua extensions
contributed by the Ceph community. This allows new object interfaces to be
dynamically loaded into the system and modified at runtime, resulting in a
object storage API with economy of expression, which at the same time provides
the full set of features of the base object class. New object interfaces that
are expressed in thousands of lines of code can be implemented in approximately
an order of magnitude less code~\cite{geambasu_comet_2010}.

>>>>

%\usepackage{fullpage}
%\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
%\usepackage{amssymb,amsmath}
%\usepackage{ifxetex,ifluatex}
\usepackage{amsmath}
%\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{listings}
%\usepackage{amssymb}
\usepackage{pifont}
\usepackage{color}
\newcommand{\cmark}{\ding{51}}%
\usepackage[font=footnotesize,labelfont=bf]{caption}

@@

\begin{table*}
\centering
\begin{tabular}{  l | l | l | l }
\multicolumn{4}{c}{\Large \textbf{Common Internal Abstractions}} \\
\multicolumn{4}{c}{} \\
\textbf{Abstraction}                    &
\textbf{Example in Production Systems}  &
\textbf{Example in Ceph}                &
\textbf{Provided Primitives}            \\ \hline
{\it Service Metadata}
  & Zookeeper, Chubby coordination~\cite{hunt_zookeeper_2010,website:chubby}
  & cluster state management~\cite{website:ceph-mon}
  & consensus \& consistency
  \\
{\it Shared Resource}
  & MPI collective IO, burst
  & POSIX metadata protocols~\cite{CITEME}
  & serialization \& batching
  \\
{\it Object \& Data}
  & Swift in situ storage/compute~\cite{website:zerocloud}
  & object interface classes~\cite{website:cls-lua}
  & transaction \& atomicity
  \\
Durability
  & S3/Swift interfaces (RESTful API)
  & object store library~\cite{weil_rados_2007}
  & interface to persistence
  \\
Load Balancing
  & VMWare's VM migration~\cite{vmware-drs,gulati:hotcloud2011-cloud-resource-management} 
  & migration in metadata cluster~\cite{weil:sc2004-dyn-metadata}
  & migration \& sampling
  \\
\end{tabular}
\caption{The same ``internal abstractions" are common across large-scale
systems because they provide primitives that solve general distributed systems
problems.  Here we list examples of what these internal abstractions are used
for in ``production systems" and in Ceph.  Malacology provides these internal
abstractions as interfaces that higher level applications can use; {\it
italicized abstractions} are interfaces contributed in this paper.}
\label{table:examples}
\end{table*}

@@

The default behavior of the monitor can be seen as a Paxos-based notification
system, similar to the one introduced in~\cite{burrows_chubby_2006}, allowing
clients to identify when new values (termed epochs in Ceph) are associated to
given maps.  While Ceph does not expose this service directly, a key-value
service designed for managing configuration metadata that is built on top of
the consensus engine is an example of a high-level service within Ceph that
re-uses existing abstractions.  While a key-value service is generally useful,
it doesn't provide many of the useful services hidden within the monitoring
framework that would be required for applications with more demanding
requirements, such as creating arbitrary maps with application-specific
semantics and interfaces. Since the monitor is intended to be out of high-performance I/O
paths, a general guideline is to make use of this functionality infrequently
and to assign small values to maps.

\paragraph*{Malacology:} Malacology exposes a strongly-consistent view of
time-varying service metadata as a service rather than a hidden internal
component. Malacology provides a generic API for adding arbitrary values to
existing subsystem cluster maps. As a consequence of this, applications can
define simple but useful service-specific logic to the strongly-consistent
interface, such as authorization control (just specific clients can write new
values) or to trigger actions based on specific values (e.g. sanitize values).
The higher level services we implement in \S\ref{sec:services} make use of this
functionality to register, version and propagate dynamic code (Lua scripts) for
new object interfaces defined in storage daemons (\S\ref{object-data-interface}) and
policies in the load balancer \S\ref{malacology:mds}).  Using this service
guarantees that interface definitions are not only made durable, but are
transparently and consistently propagated throughout the cluster so that
clients are properly synchronized with the latest interfaces.

@@

\subsection{Object I/O Interfaces}
\label{object-data-interface}

@@

An object interface is a plugin structured in a similar way to that of an RPC
in which a developer creates a named function within the cluster that clients
may invoke. In the case of Ceph each function is implicitly run within the
context of an object specified when the function is called. Developers of
object interfaces express behavior by creating a composition of native
interfaces or other custom object interfaces, and handle serialization of
function input and output.
A wide range of native interfaces are available to developers such as reading
and write to a byte stream, controlling object snapshots and clones,
and accessing a sorted key-value database. These native object interfaces
may be transactionally composed along with application specific logic to
create interfaces with a rich set of semantics.
An example is the use of a read-modify-write operation to perform consistent
object updates across the byte stream and key-value database interfaces
without relying on complex client-driven concurrency control.

@@

To address these concerns, Malacology takes advantage of Lua extensions
contributed by the Ceph community. This allows new object interfaces to be
dynamically loaded into the system and modified at runtime, resulting in a
object storage API with economy of expression, which at the same time provides
the full set of features of the base object class. New object interfaces that
are expressed in thousands of lines of code can be implemented in approximately
an order of magnitude less code~\cite{geambasu_comet_2010}. While the use of
Lua does not prevent deployment of malicious code, certain types of coding
mistakes can handled gracefully, and access policies are used to restrict the
feature to trusted users.
